---
title: "Learning Novel Categories through Background Knowledge Using Generic Statements"
author: "Xiuyuan Zhang & Dan Yurovsky"
date: "4/17/2018"
fontsize: 11pt
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
fig_crop: false
geometry: margin=0.75in
header-includes:
  - \usepackage{pdfpages}
---
## Hypothesis
In a speaker-listner interaction scenario, where the speaker utters a true generic statement '$C$(category) are $F$(feature),' we hypothesize that, when $C$ is a novel category, the listener uses her own background knowledge to infer the prevalence rate of feature $F$ in category $C$ upon hearing the generic. In our current paradigm, we provide participants a familiar category $C_{familiar}$, $C_{familiar}$ serving as background knowledge.

## Conditions
The table below includes our feature selection, its corresponding comparison categories (chosen based on our estimate of their low, medium, and high prevalence rate) and novel categories.  

Feature | Alternative Comparison Categories | Novel Category
friendly| Puppies (H), Goats (M), Squirrels (L) | Feps 
tasty| Pizzas (H), Fruits (M), Vegetables (L) | Kobas 
heavy| Trucks (H), Stones (M), Bikes (L) | Dands 

(H = high prevalence, M = medium prevalence, L = low prevalence )  

## Setup
We run three separate survey studies on Amazon Mechanical Turk. All three surveys provide participants a narrative that introduces them to an imaginary country, Akar. Sample questions from all three surveys are provided in the section below. The first survey recorded participants's evaluation of a given generic statement as True or False as well as their prevalence rate estimates for all abovementioned 9 categories (3 per feature.) The second survey introduced a novel category $C_{novel}$ along with a familiar comparison category $C_{familiar}$, then asked participants to estimate the prevalence rate of the feature $F$ in novel category $C_{novel}$. The third survey is similar to the second, with the difference that we only stated '$C_{novel}$ are like $C_{familiar}$.' before asking participants to estimate the prevalance rate of feature $F$ for $C_{novel}$. This survey serves as a sanity check, checking whether participants treat $C_{novel}$ as equivalent to $C_{familiar}$ and provide a smiliar rather than higher estimate for $C_{novel}$ comparing to estimates for $C_{familiar}$.  


## Below are two examples of the MTurk survey that we run:  
1. Getting the baseline prevalence rate for familiar comparison categories.
\includegraphics{survey_screenshots/baseline-021118/baseline_narrative.png}
\includegraphics{survey_screenshots/baseline-021118/baseline_generic_eval.png}
\includegraphics{survey_screenshots/baseline-021118/baseline_p_estimation.png}

2. Introducing a novel category with a generic statement, provding participants familiar comparison categories.
\includegraphics{survey_screenshots/explicit-generic-021118/explicit_generic_narrative.png}
\includegraphics{survey_screenshots/explicit-generic-021118/explicit_generic_p_estimation.png}

## Results





## Data Analysis and Plots

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#### Load libraries
```{r load_libraries, message = F, warning = F}
library(tidyverse)
library(lubridate)
library(lme4)
library(DT)
library(ggpirate)
library(gridExtra)

theme_set(theme_classic(base_size = 14))
```

#### read in data
```{r, message = F}
### baseline ###
data_baseline <- read_csv("baseline-survey110218/data/020818baseline-anonymized-data.csv")
### explicit generic ###
data_generic <- read_csv("generic-survey110218/data/020818generic-anonymized-data.csv")
### implicit generic ###
data_implicit <- read_csv("implicit-generic022318/data/022318implicit-generic-anonymized-data.csv")
```

#### filter participants who passed attention check 
```{r}
### baseline ###
qualtrics_filtered_baseline <- data_baseline %>%
  filter(Q8 == "friendly,tasty,heavy")
### explicit generic ###
qualtrics_filtered_generic <- data_generic %>%
  filter(Q10 == "kobas,feps,dands")
### implicit generic ###
qualtrics_filtered_implicit <- data_implicit %>%
  filter(Q10 == "kobas,feps,dands")
```


#### Munge data
In all three surveys, the categories and features we chose are consistent.
```{r}
# use to group different levels
high_objects <- c("puppies","trucks","pizzas")
med_objects <- c("goats", "rocks", "fruits")
low_objects <- c("squirrels", "bikes", "vegetables")
features <- c("friendly", "heavy", "tasty")

# features and objects for the survey
objects <- data_frame(type = "high", object = high_objects,
                      feature = features) %>%
  bind_rows(data_frame(type = "medium", object = med_objects,
                       feature = features)) %>%
  bind_rows(data_frame(type = "low", object = low_objects,
                       feature = features))


# get data for each of the three conditions
### baseline ###
q1_baseline <- qualtrics_filtered_baseline %>%
  select(id, L_feature, L_object, Q1, Q2_1) %>%
  rename(feature = L_feature, baseline_object = L_object, truefalse_response = Q1, percent_response = Q2_1)

q2_baseline <- qualtrics_filtered_baseline %>%
  select(id, M_feature, M_object, Q3, Q4_1) %>%
  rename(feature = M_feature, baseline_object = M_object, truefalse_response = Q3, percent_response = Q4_1)

q3_baseline <- qualtrics_filtered_baseline %>%
  select(id, H_feature, H_object, Q5, Q6_1) %>%
  rename(feature = H_feature, baseline_object = H_object, truefalse_response = Q5, percent_response = Q6_1)

### explicit generic ###
colnames(qualtrics_filtered_generic)[colnames(qualtrics_filtered_generic) == "Duration (in seconds)"] <- "time_spent"

# get data for each of the three conditions
q1_generic <- qualtrics_filtered_generic %>%
  select(id, L_feature, L_comparison, L_novel, Q2_1, time_spent) %>%
  rename(feature = L_feature, baseline_object = L_comparison, novel_object = L_novel, percent_response = Q2_1)

q2_generic <- qualtrics_filtered_generic %>%
  select(id, M_feature, M_comparison, M_novel, Q5_1, time_spent) %>%
  rename(feature = M_feature, baseline_object = M_comparison, novel_object = M_novel,percent_response = Q5_1)

q3_generic <- qualtrics_filtered_generic %>%
  select(id, H_feature, H_comparison, H_novel, Q6_1, time_spent) %>%
  rename(feature = H_feature, baseline_object = H_comparison, novel_object = H_novel, percent_response = Q6_1)

### implicit generic ###
colnames(qualtrics_filtered_implicit)[colnames(qualtrics_filtered_implicit) == "Duration (in seconds)"] <- "time_spent"

# get data for each of the three conditions
q1_implicit <- qualtrics_filtered_implicit %>%
  select(id, L_feature, L_comparison, L_novel, Q2_1, time_spent) %>%
  rename(feature = L_feature, baseline_object = L_comparison, novel_object = L_novel, percent_response = Q2_1)

q2_implicit <- qualtrics_filtered_implicit %>%
  select(id, M_feature, M_comparison, M_novel, Q5_1, time_spent) %>%
  rename(feature = M_feature, baseline_object = M_comparison, novel_object = M_novel,percent_response = Q5_1)

q3_implicit <- qualtrics_filtered_implicit %>%
  select(id, H_feature, H_comparison, H_novel, Q6_1, time_spent) %>%
  rename(feature = H_feature, baseline_object = H_comparison, novel_object = H_novel, percent_response = Q6_1)

# combine
### baseline ###
response_data_baseline <- bind_rows(q1_baseline, q2_baseline, q3_baseline) %>%
  mutate(type = if_else(baseline_object %in% high_objects, "high",
                        if_else(baseline_object %in% med_objects, "medium","low"))) %>%
  mutate(type = factor(type, levels = c("low", "medium", "high")))
### explicit generic ###
response_data_generic <- bind_rows(q1_generic, q2_generic, q3_generic) %>%
  mutate(type = if_else(baseline_object %in% high_objects, "high",
                        if_else(baseline_object %in% med_objects, "medium","low"))) %>%
  mutate(type = factor(type, levels = c("low", "medium", "high")))
### implicit generic ###
response_data_implicit <- bind_rows(q1_implicit, q2_implicit, q3_implicit) %>%
  mutate(type = if_else(baseline_object %in% high_objects, "high",
                        if_else(baseline_object %in% med_objects, "medium","low"))) %>%
  mutate(type = factor(type, levels = c("low", "medium", "high")))


### baseline ###
# filter to include only participants who chose "Yes" to the question on evaluating generic statement
response_filtered_yes_baseline <- response_data_baseline %>%
  filter(truefalse_response == "Yes")

### explicit generic ###
# filter participants based on their time of survey completion
response_data_control_for_time_generic <- response_data_generic %>%
  filter(time_spent > 45)

### implicit generic ###
# filter participants based on their time of survey completion
response_data_control_for_time_implicit <- response_data_implicit %>%
  filter(time_spent > 45)
```


```{r}
head(response_data_control_for_time_generic)
head(response_filtered_yes_baseline)

#with feature + type
response_filtered_yes_baseline %>%
  group_by(id,type, feature) %>%
  summarize(percent_response=mean(percent_response), n()) %>%
  group_by(feature,type) %>%
  summarize(mean=mean(percent_response), std_err=sd(percent_response)/sqrt(length(percent_response)), n())

#just type
full_data_yes <- response_filtered_yes_baseline %>%
  select(-truefalse_response) %>%
  mutate(condition='baseline') %>%
  bind_rows(response_data_control_for_time_generic %>% mutate(condition='generic'))
full_data_yes_by_type <- full_data_yes %>%
  group_by(id,type,condition) %>%
  summarize(percent_response=mean(percent_response), n()) %>%
  group_by(condition,type) %>%
  summarize(mean=mean(percent_response), std_err=sd(percent_response)/sqrt(length(percent_response)), n())


ggplot(data=full_data_yes_by_type, aes(x=type, y=mean, color=condition)) + 
  geom_pointrange(aes(ymin = mean-std_err, ymax = mean+std_err), 
                  position=position_dodge(.5)) +
  coord_cartesian(ylim=c(0,100))

# NOT FILTERING YES, ALL BASELINE
response_data_baseline %>%
  group_by(id,type, feature) %>%
  summarize(percent_response=mean(percent_response), n()) %>%
  group_by(feature,type) %>%
  summarize(mean=mean(percent_response), std_err=sd(percent_response)/sqrt(length(percent_response)), n())

#just type
library(tidyboot)
full_data <- response_data_baseline %>%
  select(-truefalse_response) %>%
  mutate(condition='baseline') %>%
  bind_rows(response_data_control_for_time_generic %>% mutate(condition='novel'))
full_data_by_type <- full_data %>%
  group_by(condition,type) %>%
  tidyboot_mean(percent_response)
  
  # summarize(mean=mean(percent_response), std_err=sd(percent_response)/sqrt(length(percent_response)), n())
  


ggplot(data=full_data_by_type, aes(x=type, y=mean, fill=condition)) + 
  geom_bar(stat="identity", position="dodge")+
    geom_linerange(aes(ymin = ci_lower, ymax = ci_upper), shape = 20, size = 0.4,position=position_dodge(.9)) +
  coord_cartesian(ylim=c(40,100)) +
  ylab("Percent(%)") +
  xlab("Feature Prevalence Estimation by Level") +
  ggtitle("Mean Feature Prevalence Estimation")

```


```{r}
# plot - pirate
### baseline ###
ggplot() + 
  geom_pointrange(data = response_filtered_yes_baseline, mapping = (aes(x = type, y = mean(percent_response), ymin = , ymax = )) )


p1_baseline <- ggplot(response_data_baseline, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Baseline - All") + 
  geom_pirate()

p2_baseline <- ggplot(response_filtered_yes_baseline, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Baseline - Yes-Only") +
  geom_pirate()

### explicit generic ###
p1_generic<- ggplot(response_data_generic, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Explicit Generic - All") + 
  geom_pirate()

p2_generic <- ggplot(response_data_control_for_time_generic, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Explicit Generic - Time Spent > 45") + 
  geom_pirate()

### implicit generic ###
p1_implicit<- ggplot(response_data_implicit, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Implicit Generic - All") + 
  geom_pirate()

p2_implicit <- ggplot(response_data_control_for_time_implicit, aes(x = type, y = percent_response, color = feature, fill = feature)) + 
  facet_wrap(~ feature) +
  ggtitle("Implicit Generic - Time Spent > 45") + 
  geom_pirate()

#### arrange graphs
#grid.arrange(p1_generic, p2_generic, ncol = 2)
#grid.arrange(p1_baseline, p2_baseline, ncol = 2)
#grid.arrange(p1_implicit, p2_implicit, ncol = 2)
# put all graphs together
#grid.arrange(p1_baseline, p2_baseline, p1_implicit, p2_implicit, p1_generic, p2_generic, ncol = 2)
# put baseline-all, implicit-generic time spent>45, explicit generic time spent >45
#grid.arrange(p1_baseline, p2_implicit, p2_generic, ncol = 3)
# put baseline-Yes, implicit-generic time spent>45, explicit generic time spent >45
#grid.arrange(p2_baseline, p2_implicit, p2_generic, ncol = 3)
```

