---
title: "Novel Generic Demographic Control by Gender and Age"
author: "Xiuyuan Zhang and Dan Yurovsky"
date: "5/8/2018"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load libraries
```{r load_libraries, message = F, warning = F}
library(tidyverse)
library(lubridate)
library(lme4)
library(DT)
library(ggpirate)
library(gridExtra)
library(knitr)
library(tidyboot)

theme_set(theme_classic(base_size = 14))
```

### Read in anonymized data

```{r, message = F}
data_novel <- read_csv("data/05082018_novel_anonymized_data.csv")
```
The total number of participants we get is `r nrow(data)`. Out of 200 participants, 1 participant did not provide a valid survey code provided by our random survey code generator.

```{r}
qualtrics_filtered <- data_novel %>%
  filter(attention_check == "watch nightly news on tv,like online shopping,drink coffee,like desserts,drive to work,like computer and video games")
```

Filter peole who passed the attention check, result: n = `r nrow(qualtrics_filtered)` (out of `r nrow(data)` )

Rename questions
```{r rename}
tidy_data <- qualtrics_filtered %>%
  filter(gender != "Other/Non-conforming") %>%
  rename(male_high = gender_videogame_1, male_low = gender_desserts_1, age_high = age_nightlynews_1, age_low = age_onlineshopping_1, 
         control_high = control_drive_1, control_low = control_coffee_1) %>%
  mutate(gender = factor(gender, levels = c("Female", "Male"), 
                         labels = c("female", "male"))) %>%
  select(male_high, male_low, age_high, age_low, control_high, control_low, gender, age)
```

Basic demographics
```{r demos}
tidy_data %>%
  group_by(gender) %>%
  summarise(n = n()) %>%
  kable()

tidy_data %>%
  ggplot(aes(x = age)) + 
  geom_histogram(binwidth = 5, fill = "white", color = "black")
```

Looks like Data are really thin past 60, so cut there
```{r filtered_data}
filtered_data <- tidy_data %>%
  filter(age < 60) %>%
  mutate(age_bin = factor(age > median(age), labels = c("younger", "older")))

filtered_data %>%
  group_by(gender, age_bin) %>%
  summarise(n = n(), age = mean(age)) %>%
  kable()
```

By filtering less than 50, we lost `r nrow(tidy_data) - nrow(filtered_data)` people

Convert to longform
```{r long_data}
long_data <- filtered_data %>%
  ungroup() %>%
  mutate(id = 1:n()) %>%
  gather(question, prevalence, male_high, male_low, age_high, age_low, 
         control_high, control_low) %>%
  separate(question, sep = "_", into = c("question", "level"))
```

Gender
```{r gender}
gender_outcomes <- long_data %>%
  filter(question == "male") %>%
  group_by(level, gender) %>%
  tidyboot_mean(prevalence) 

gender_outcomes %>%
  ungroup() %>%
  mutate(level = factor(level, levels = c("low", "high"),
                        labels = c("like desserts", "play computer and video games"))) %>%
  ggplot(aes(x = level, y = empirical_stat, ymax = ci_upper, ymin = ci_lower, 
             color = gender, label = gender)) + 
  geom_pointrange(position = position_dodge(.25)) +
  #geom_dl(method =list(dl.trans(x= x -1), "first.points", cex=1)) +
  theme(legend.position = "none") + 
  geom_text()
```

Age
```{r age}
age_outcomes <- long_data %>%
  filter(question == "age") %>%
  group_by(level, age_bin) %>%
  tidyboot_mean(prevalence) 

age_outcomes %>%
  ggplot(aes(x = age_bin, y = empirical_stat, ymax = ci_upper, 
             ymin = ci_lower, color = level)) + 
  geom_pointrange(position = position_dodge(.5))
```

Control
```{r control}
control_gender <- long_data %>%
  filter(question == "control") %>%
  group_by(level, gender) %>%
  tidyboot_mean(prevalence) 

control_age <- long_data %>%
  filter(question == "control") %>%
  group_by(level, age_bin) %>%
  tidyboot_mean(prevalence) 

control_gender %>%
  ggplot(aes(x = gender, y = empirical_stat, ymax = ci_upper, ymin = ci_lower, 
             color = level)) + 
  geom_pointrange(position = position_dodge(.5))

control_age %>%
  ggplot(aes(x = age_bin, y = empirical_stat, ymax = ci_upper, ymin = ci_lower, 
             color = level)) + 
  geom_pointrange(position = position_dodge(.5))
```

Models
```{r single_q_models}
lmer(prevalence ~ scale(age) * level + (1|id), 
     data = filter(long_data, question == "age")) %>%
  summary()

lmer(prevalence ~ gender * level + (1|id), 
     data = filter(long_data, question == "male")) %>%
  summary()

lmer(prevalence ~ gender * level + age*level + (1|id), 
     data = filter(long_data, question == "control")) %>%
  summary()
```


The big model 
```{r big_model}
big_model <- long_data %>%
  mutate(question = factor(question, levels = c("control", "age", "male"))) %>%
  lmer(prevalence ~ level * age * question + level * gender * question + 
         (1|id), data = .) %>%
  summary()
```