---
title             : "Interpretation of Generic Language is Dependent on Listener's Background Knowledge"
shorttitle        : "Title"

author: 
  - name          : "Xiuyuan Zhang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "xiuyuanzhang@uchicago.edu"
  - name          : "Daniel Yurovsky"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "University of Chicago"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  Generic language, like "birds lay eggs" or "dogs bark" are simple and ubiquitous in naturally produced speech. However, the inherent vagueness of generics makes their interpretation highly context-dependent. Building on work by @tessler2019 showing that generics can be thought of as inherently relative (i.e. more birds lay eggs than you would expect), we explore the consequences of different implied comparison categories on the interpretation of novel generics. In Experiments 1 and 2, we manipulated the set of categories salient to a listener by directly providing them the comparison sets. In Experiments 3 and 4, we collected participants’ demographic information and used these naturally occurring differences as a basis for differences in the participants' comparison sets. Results from all four studies confirmed our hypothesis that the prevalence of a feature in different comparison categories changes people' estimations of the feature's prevalence in novel categories. These results, highlighting how context-sensitive interpretations of generic language are to listeners' prior knowledge, suggest a possible source for *well-intentioned* miscommunications, where conversational partners are cooperative during a discourse but are led by their different backgrounds to make dissimilar inferences of the same statement. 
  
keywords          : " generics; semantics; meaning; learning; Bayesian inference"
wordcount         : "X"

bibliography      : ["generics.bib"]

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : yes

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r, libraries}
library(tinytex)
library(png)
library(jpeg)
library(grid)
library(xtable)
library(tidyverse)
library(lubridate)
library(lme4)
library(lmerTest)
library(knitr)
library(tidyboot)
library(ggrepel)
library(ggridges)
library(here)
library(broom)
library(broom.mixed)
library(viridis)
library(papaja)
library(ggthemes)

theme_set(theme_classic(base_size = 10))

options(digits=2)
```

# experiment 1 - experimentally manipulated priors (incl. baseline and novel)

```{r e1_data}
#### read in data
### baseline ###
data_baseline <- read_csv(here("baseline-survey110218/data/020818baseline-anonymized-data.csv"))
### explicit generic ###
data_generic <- read_csv(here("generic-survey110218/data/020818generic-anonymized-data.csv"))

#### filter participants who passed attention check 
### baseline ###
qualtrics_filtered_baseline <- data_baseline %>%
  filter(Q8 == "friendly,tasty,heavy")
### explicit generic ###
qualtrics_filtered_generic <- data_generic %>%
  filter(Q10 == "kobas,feps,dands")

#### Munge data
### In both surveys, the categories and features we chose are consistent.
# use to group different levels
high_objects <- c("puppies","trucks","pizzas")
med_objects <- c("goats", "rocks", "fruits")
low_objects <- c("squirrels", "bikes", "vegetables")
features <- c("friendly", "heavy", "tasty")

# features and objects for the survey
objects <- data_frame(type = "high", object = high_objects,
                      feature = features) %>%
  bind_rows(data_frame(type = "medium", object = med_objects,
                       feature = features)) %>%
  bind_rows(data_frame(type = "low", object = low_objects,
                       feature = features))

# get data for each of the three conditions
### baseline ###
q1_baseline <- qualtrics_filtered_baseline %>%
  select(id, L_feature, L_object, Q1, Q2_1) %>%
  rename(feature = L_feature, baseline_object = L_object, truefalse_response = Q1, percent_response = Q2_1)

q2_baseline <- qualtrics_filtered_baseline %>%
  select(id, M_feature, M_object, Q3, Q4_1) %>%
  rename(feature = M_feature, baseline_object = M_object, truefalse_response = Q3, percent_response = Q4_1)

q3_baseline <- qualtrics_filtered_baseline %>%
  select(id, H_feature, H_object, Q5, Q6_1) %>%
  rename(feature = H_feature, baseline_object = H_object, truefalse_response = Q5, percent_response = Q6_1)

### explicit generic ###
colnames(qualtrics_filtered_generic)[colnames(qualtrics_filtered_generic) == "Duration (in seconds)"] <- "time_spent"

# get data for each of the three conditions
q1_generic <- qualtrics_filtered_generic %>%
  select(id, L_feature, L_comparison, L_novel, Q2_1, time_spent) %>%
  rename(feature = L_feature, baseline_object = L_comparison, novel_object = L_novel, percent_response = Q2_1)

q2_generic <- qualtrics_filtered_generic %>%
  select(id, M_feature, M_comparison, M_novel, Q5_1, time_spent) %>%
  rename(feature = M_feature, baseline_object = M_comparison, novel_object = M_novel,percent_response = Q5_1)

q3_generic <- qualtrics_filtered_generic %>%
  select(id, H_feature, H_comparison, H_novel, Q6_1, time_spent) %>%
  rename(feature = H_feature, baseline_object = H_comparison, novel_object = H_novel, percent_response = Q6_1)

# combine
### baseline ###
response_data_baseline <- bind_rows(q1_baseline, q2_baseline, q3_baseline) %>%
  mutate(type = if_else(baseline_object %in% high_objects, "high",
                        if_else(baseline_object %in% med_objects, "medium","low"))) %>%
  mutate(type = factor(type, levels = c("low", "medium", "high")))
### explicit generic ###
response_data_generic <- bind_rows(q1_generic, q2_generic, q3_generic) %>%
  mutate(type = if_else(baseline_object %in% high_objects, "high",
                        if_else(baseline_object %in% med_objects, "medium","low"))) %>%
  mutate(type = factor(type, levels = c("low", "medium", "high")))

#### Plot for CogSci
exp1_old_long_data <- response_data_baseline %>%
  mutate(condition = "baseline")

exp1_new_long_data <- response_data_generic %>%
  mutate(condition = "novel")
  
exp1_all_long_data <- bind_rows(exp1_new_long_data, exp1_old_long_data) %>%
  select(-truefalse_response, -time_spent)

exp1_empirical_stats <- exp1_all_long_data %>%
  group_by(condition, type) %>%
  tidyboot_mean(percent_response) 
```

```{r}
response_filtered_yes_baseline <- response_data_baseline %>%
  filter(truefalse_response == "Yes") %>%
  mutate(true = "baseline_yes")

empirical_stats_filtered_yes_baseline <- response_filtered_yes_baseline %>%
  group_by(type) %>%
  tidyboot_mean(percent_response)

exp1_baseline_lmer <- exp1_old_long_data %>%
  mutate(id = paste0(condition, "_", id)) %>%
  lmer(percent_response/100 ~ type * truefalse_response + (1|id) + (1|feature), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

exp1_baseline_all_lmer <- exp1_old_long_data %>%
  mutate(id = paste0(condition, "_", id)) %>%
  lmer(percent_response/100 ~ type + (1|id) + (1|feature), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)

# add model for only responses that endorsed the generic
exp1_baseline_endorsed_lmer <- response_filtered_yes_baseline %>%
  lmer(percent_response/100 ~ type + (1|id) + (1|feature), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)
  

```


```{r}
exp1_lmer <- exp1_all_long_data %>%
  mutate(id = paste0(condition, "_", id)) %>%
  lmer(percent_response/100 ~ type * condition + (1|id) + (1|feature), data = .) %>%
  tidy() %>%
  filter(effect == "fixed") %>%
  select(-effect, -group)
```

# experiment 2 - naturally occurring priors & simulations (incl. baseline)
```{r Exp2and3-data}

data_new <- read_csv(here("/demographic_generic/novel_generic/data/01102019_people_novel_habit_anonymized_data.csv"))
data_old <- read_csv(here("/demographic_generic/baseline-people-habits/data/10312018_people_habit_anonymized_data.csv"))

# filter by condition: passing attention check
old_attnCheckAnswers <- c('drink coffee','cook at home', 'go to the gym', 'drive to work')

old_qualtrics_filtered <- data_old %>%
    rowwise() %>%
  mutate(attention_check = (strsplit(attention_check, ','))) %>%
  mutate(attnTrue = sum(attention_check %in% old_attnCheckAnswers),
         attnFalse= sum(!attention_check %in% old_attnCheckAnswers))%>%
  filter(attnFalse==0)

old_tidy_data <- old_qualtrics_filtered %>%
  filter(gender != "Other/Non-conforming") %>%
  mutate(gender = factor(gender, levels = c("Female", "Male"), labels = c("female", "male")))

old_filtered_data <- old_tidy_data %>%
  filter(age < 60) %>%
  mutate(age_bin = if_else(age > median(old_tidy_data$age), "older", "younger"),
         politics_bin = if_else(politics_1 > median(old_tidy_data$politics_1), 
                                "conservative", "liberal"))

new_attnCheckAnswers <- c('like big cities','cook at home', 'go to the gym', 'consume dairy products')

new_qualtrics_filtered <- data_new %>%
    rowwise() %>%
  mutate(attention_check = (strsplit(attention_check, ','))) %>%
  mutate(attnTrue = sum(attention_check %in% new_attnCheckAnswers),
         attnFalse= sum(!attention_check %in% new_attnCheckAnswers))%>%
  filter(attnTrue ==4 & attnFalse==0)

new_tidy_data <- new_qualtrics_filtered %>%
  filter(gender != "Other/Non-conforming") %>%
  mutate(gender = factor(gender, levels = c("Female", "Male"), labels = c("female", "male"))) 

new_filtered_data <- new_tidy_data %>%
  filter(age < 60) %>%
  mutate(age_bin = if_else(age > median(old_tidy_data$age), "older", "younger"),
         politics_bin = if_else(politics_1 > median(old_tidy_data$politics_1), 
                                "conservative", "liberal"))

old_long_data <- old_filtered_data %>%
  select(big_cities_1, computer_preference_1, cook_at_home_1,own_homes_1, dairy_products_1, go_to_gym_1, gender, age_bin, politics_bin, id) %>%
  gather(question, response, big_cities_1, computer_preference_1, cook_at_home_1,own_homes_1, dairy_products_1, go_to_gym_1)

new_long_data <- new_filtered_data %>%
  select(big_cities_1:go_to_gym_1, 
         gender, age_bin, politics_bin, id)%>%
  gather(question, response, big_cities_1:go_to_gym_1)

#### cor
new_data <- new_long_data %>% 
  group_by(id) %>%
  mutate(response = scale(response)) %>%
  group_by(gender, age_bin, politics_bin, question) %>%
  summarise(mean = mean(response, na.rm = T)) %>%
  mutate(data = "new")

old_data <- old_long_data %>%
  group_by(id) %>%
  mutate(response = scale(response)) %>%
  group_by(gender, age_bin, politics_bin, question) %>%
  summarise(mean = mean(response)) %>%
  mutate(data = "old")

all_data <- bind_rows(new_data, old_data) %>%
  group_by(question) %>%
  spread(data, mean) %>%
  summarise(cor = cor(new, old, use = "complete"))

t_test_cor_result <- t.test(all_data$cor)

# UNSCALED
unscaled_new_data <- new_long_data %>% 
  group_by(id) %>%
  group_by(gender, age_bin, politics_bin, question) %>%
  summarise(mean = mean(response, na.rm = T)) %>%
  mutate(data = "new")

unscaled_old_data <- old_long_data %>%
  group_by(id) %>%
  group_by(gender, age_bin, politics_bin, question) %>%
  summarise(mean = mean(response)) %>%
  mutate(data = "old")

unscaled_all_data <- bind_rows(unscaled_new_data, unscaled_old_data) %>%
  group_by(question) %>%
  spread(data, mean) %>%
  summarise(cor = cor(new, old, use = "complete"))

unscaled_all_data_mean <- bind_rows(unscaled_new_data, unscaled_old_data) %>%
  group_by(question) %>%
  spread(data, mean)

all_data_mean <- bind_rows(new_data, old_data) %>%
  group_by(question) %>%
  spread(data, mean)

question_labels <- c(big_cities_1 = "like big cities",
                     computer_preference_1 = "prefers Macs over PCs",
                     cook_at_home_1 = "like to cook at home",
                     dairy_products_1 = "consume dairy products",
                     go_to_gym_1 = "go to the gym",
                     own_homes_1 = "own homes")
```
# experiment 3 - naturally occurring priors (incl. novel)




# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis


# Results

# Discussion


\newpage

# References
```{r create_r-references}
r_refs(file = "r-references.bib")
```

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id = "refs"></div>
\endgroup
